CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability and GPUs

### 2019-03-22 gpus/paper.tex
some fixes

@@

The {\tt flame\_wave} problem in \castro\ was described in
\cite{astronum:2018}.  This problem explores the lateral propagation
of a helium deflagration across a neutron star in a plane-parallel
atmosphere.  The Castro PPM CTU hydrodynamics solver is used, with a
constant gravitational acceleration, and the problem is solved in the
corotating frame, where the Coriolis forces acts to balance the
lateral spreading in the atmosphere via geostrophic balance.  For the
microphysics, we use the general stellar equation of state of
\citep{timmes_swesty:2000} and the stellar conductivity described in
\citep{Timmes00}.  The science goal of the problem is to understand the
dynamics of a resolved burning front in X-ray bursts.  For this work,
this problem serves as an ideal reacting flow problem to benchmark
GPUs with.  All of the necessary physics: hydrodynamics, equation of
state, thermal conductivities, reactions, hydrodynamic source terms,
and thermal diffusion are run on the GPU.  We look at two different
reaction networks, a 7-isotope alpha network and a 13-isotope alpha
network~\cite{iso7}.

@@

\acknowledgements \castro\ is available at
\url{http://github.com/AMReX-Astro/Castro}.  The work at Stony Brook
was supported by DOE/Office of Nuclear Physics grant DE-FG02-87ER40317
and NSF award AST-1211563.  An award of computer time was provided by
the Innovative and Novel Computational Impact on Theory and Experiment
(INCITE) program.  This research used resources of the Oak Ridge
Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No. DE-AC05-00OR22725.  In particular, we thank
OLCF for early access to the Summitdev platform, where we could
develop and debug our GPU approach.  We also thank NVIDIA Corporation
for the donation of a Titan X Pascal and Titan V used in this
research.  The GPU development of \castro\ benefited greatly from
numerous GPU hackathons arranged by OLCF.

>>>>

To understand the GPU performance of the reactions, we run a simple pure reaction test.  \MarginPar{is this {\tt test\_react}?}

@@

The {\tt flame\_wave} problem\footnote{Found in {\tt Castro/Exec/science/flame\_wave/}} in \castro\ was described in
\cite{astronum:2018}.  This problem explores the lateral propagation
of a helium deflagration across a neutron star in a plane-parallel
atmosphere.  The Castro PPM CTU hydrodynamics solver is used, with a
constant gravitational acceleration, and the problem is solved in the
corotating frame, where the Coriolis forces acts to balance the
lateral spreading in the atmosphere via geostrophic balance.  For the
microphysics, we use the general stellar equation of state of
\citep{timmes_swesty:2000} and the stellar conductivity described in
\citep{Timmes00}.  The science goal of the problem is to understand the
dynamics of a resolved burning front in X-ray bursts.  For this work,
this problem serves as an ideal reacting flow problem to benchmark
GPUs with.  All of the necessary physics: hydrodynamics, equation of
state, thermal conductivities, reactions, hydrodynamic source terms,
and thermal diffusion are run on the GPU.  We look at two different
reaction networks, a 7-isotope alpha network and a 13-isotope alpha
network~\citep{iso7}.

@@

\acknowledgements \castro\ is available at
\url{http://github.com/AMReX-Astro/Castro}.  The work at Stony Brook
was supported by DOE/Office of Nuclear Physics grant DE-FG02-87ER40317
and NSF award AST-1211563.  An award of computer time was provided by
the Innovative and Novel Computational Impact on Theory and Experiment
(INCITE) program.  This research used resources of the Oak Ridge
Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No.\ DE-AC05-00OR22725.  In particular, we thank
OLCF for early access to the Summitdev platform, where we could
develop and debug our GPU approach.  We also thank NVIDIA Corporation
for the donation of a Titan X Pascal and Titan V used in this
research.  The GPU development of \castro\ benefited greatly from
numerous GPU hackathons arranged by OLCF.
